Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-07-12 papers/EMNLP2019/reviews_author_response.txt

Fine-tuning on ManyNames for the described experiment would allow for covering all name types, but disallows a direct comparison of ManyNames against VG object names in the single label setting.
We will fine-tune models on ManyNames in the future as a means to analyse the underlying (visual) factors causing naming variation, which is beyond the scope of the present paper.

> What is the loss of training? Ground-truth targets are the actual distribution of names or top-1 names?
We did not retrain or fine-tune Bottom-up, but used the publicly available model (see Anderson et al. 2018). 
For evaluation we used both, and four different ground truth targets in total, see L680-691. Thank you for pointing out that this was unclear.

Review #3:
---
Thank you very much for your review. We will revise the presentation of the tables as you suggested.

Response to Reviewer #1:
---
In contrast to the works you list, our dataset and its analysis is not on referring expressions for objects, but on object names---i.e., words (nouns or compound nouns) which you would naturally use to name an object ("entry-level category" or "canonical name"), irrespective of whether you would use the same name for other objects in the same image (e.g., an image showing several giraffes, chairs or boys). 
It is a phenomenon underlying referring expressions. To understand how the choice of the name interacts with choosing attributes (modifiers, prepositional phrases), one needs to know which name variants exist and how they are related. 
See also the last paragraph on page 791 (page 5) in the first paper you point out (Kazemzadeh et al., 2014) for the difference of referring expressions and canonical names (entry-level categories). It also that the paper adopts two standard assumptions:
- naming variants are related hierarchically, which, as we show, is not the only relation in real-world images
- there exists an entry-level (canonical name) and we know which ones they are, they are instance-invariant

@@

Unfortunately we found existing datasets (ReferIt, those based on MSCOCO, VisualGenome descriptions) to not provide the information necessary for linguistically studying object naming (and ultimately referring expressions): 
* Regarding the ReferIt paper (Kazemzadeh et al., 2014) in particular: 
- Only 10.7% of all object instances have 2 or more referring expressions, while almost 90% has only one expression. Hence, most of the instances have one name, at most 2, i.e., provide neither name variants on the instance-level, nor is recoverable whether the chosen noun is the name one would naturally use for the instance. 
- The latter also applies to the option to use the VisualGenome object *descriptions* (as opposed to the single object *name*). 
- Among ReferIt's most frequently objects are, e.g., corner, background, head, pic, sky, foreground.

* The situation is similar with respect to the datasets based on MSCOCO (https://arxiv.org/abs/1608.00272): 
- On average, they also only have between 1.5 and 2.8 referring expressions per instance. 
- They only cover the 80 MSCOCO categories, and these are of different levels of specificity (person, dog, tie, donut, ...).

> Thus, the core question of this paper, "Do Objects in Real-World Images Have a Canonical Name?", will not impactful (at least, in the NLP community). I feel that people already know "no".
Could you please provide the corresponding references which have analyzed and shown that real-world object instances do not have a preferred name most people would agree on, such that we can refer to this in our paper?
